Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-11 main.tex
rewrote the description of clusters (incl memory-constrained)

    \subsubsection{Target computing systems}
    \skug{Check that the description of speeds and memories is plausible and consistent with experimental setup. esp check for 19200 -> 192 GB.}

    To fully benefit from the historical data, the  {\em default} experimental environment
    that we consider is a cluster based on the same six
    kinds of real-world machines that were used in the experimental evaluation in~\cite{lotaru}.
    We set the number of each kind of node to \skug{$24$ - check if this still holds }, thus having 144 processors in total. % the whole cluster.

    Each machine has a (normalized) CPU speed and a memory size (in GB), and we list them as (name, speed, memory):
    ($local$, 4, 16) -- very slow machines; ($A1$, 32, 32), ($A2$, 6, 64), ($N1$, 12, 16) -- average machines; ($N2$, 8, 8) -- machine with very small memory; and ($C2$, 32, 192) -- {\em luxury} machine with high speed and large memory
    (see Table~\ref{tab:procs} in Appendix~\ref{sub:appx-cluster-config}~\cite{daghetpart_full_version}).

    To test various settings, we also vary the cluster configuration and consider
    variants of the default cluster presented above:\\
    $\bullet$ {\em tiny}, {\em small} and {\em large} clusters. While the default cluster consists of 144 nodes (24 of each kind), we
    consider a small cluster with $18$ processors of each kind ($108$ processors in total), a tiny cluster with $72$ nodes and a
    large cluster with $36$ processors of each kind ($216$ processors in total). \skug{check for cluster sizes and naming}\\

@@

    \subsubsection{Static experiments}
    \paragraph{Tiny cluster}

>>>>

    \subsubsection{Target computing systems}
    \skug{Because of the normalized nature of the task/edge weights, I will now be saying that our larger cluster has 192 GB and it
    is represented as 192 000 (with 3 zeroes). For the memory-constrained cluster (192 00 with 2 zeroes) I will say that it has 10 times
    less memory - 19.2 GB. Other processors will be dealt with similarly.}

    To fully benefit from the historical data, the  {\em default} experimental environment
    that we consider is a cluster based on the same six
    kinds of real-world machines that were used in the experimental evaluation in~\cite{lotaru}.
    We set the number of each kind of node to $12$, thus having 72 processors in total. % the whole cluster.

    Each machine has a (normalized) CPU speed and a memory size (in GB), and we list them as (name, speed, memory):
    ($local$, 4, 16) -- very slow machines; ($A1$, 32, 32), ($A2$, 6, 64), ($N1$, 12, 16) -- average machines;
    ($N2$, 8, 8) -- machine with very small memory; and ($C2$, 32, 192) -- {\em luxury} machine with high speed and
    large memory (see Table~\ref{tab:procs}).

    \begin{table}[htb]
        \begin{center}
            \begin{tabular}{rcc}
                \toprule
                Processor name %& Amount
                &  CPU speed (GHz)  &Memory size (GB) \\
                \midrule
                local                    & 4                    & 16     \\
                A1                      & 32                   & 32     \\
                A2                      & 6                    & 64     \\
                N1                      & 12                   & 16     \\
                N2                      & 8                    & 8      \\
                C2                      & 32                   & 192    \\
                \bottomrule
            \end{tabular}
        \end{center}
        \caption{Cluster configuration (default).}
        \label{tab:procs}
    \end{table}

    To more constrained settings, we also vary the cluster configuration and consider
    a memory-constrained cluster.
    Like the default cluster, it consists of 72 nodes (12 of each kind), but we
    give each node $10$ times less memory.
    So, the {\em luxury} machine $C2$ has $19.2$~GB memory in this setting instead of $192$~GB, $A2$ has $6.4$~\GB instead
    of $64$~GB etc.
    The processor speeds and their relations stay unchanged.

@@

    \subsubsection{Static experiments}
    \paragraph{Memory-constrained cluster}
